---
title: "p8105_hw5_jdv2118"
author: "Justin Vargas"
output: github_document
---
# Loading Libraries and Figure Options

```{r, message = FALSE, warning = FALSE}

library(tidyverse)

library(dplyr)

library(broom)

library(knitr)

opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r, message = FALSE, warning = FALSE}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

# Problem 2

```{r, message = FALSE}
raw_data = 
  read_csv("data/homicide_data.csv") 

homicide =
  raw_data %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    result = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved",
      disposition == "Open/No arrest" ~ "unsolved")
  ) %>% 
  select(city_state, result) %>% 
  filter(city_state != "Tulsa, AL")
```

The raw data consists of `r ncol(raw_data)` variables, which are uid, reported_date, victim_last, victim_first, victim_race, victim_age, victim_sex, city, state, lat, lon, and disposition.  The raw data also consists of `r nrow(raw_data)` rows.

The following code is used to create a new dataframe with two new variables, unsolved_homicides and total_homicides, which entail the number of unsolved homicides and the total number of homicides, respectively.

```{r, message = FALSE}
homicide_info = 
  homicide %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved_homicides = sum(result == "unsolved"),
    total_homicides = n()
  )
```

The following code is used to estimate the proportion of homicides that are unsolved for Baltimore, MD, through the use of a prop.test.

```{r, message = FALSE}
prop.test(
  homicide_info %>% 
  filter(city_state == "Baltimore, MD") %>% 
  pull(unsolved_homicides), 
  homicide_info %>% 
  filter(city_state == "Baltimore, MD") %>% 
  pull(total_homicides)) %>% 
  tidy()
```

```{r, message = FALSE}
results = 
  homicide_info %>% 
  mutate(
    prop_tests = map2(.x = unsolved_homicides, .y = total_homicides,          ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)

results
```

```{r, message = FALSE}
homicide_plot =
  results %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(
    x = "City and State", 
    y = "Estimate",
)

homicide_plot
```

# Problem 3

The following code is used to create a simulation function with the following design elements of n = 30 and sigma = 5.

```{r}
set.seed(3)

simulation_function = function(n = 30, mu, sigma = 5) {
  
  x = rnorm(n, mean = mu, sd = sigma)
  t_test = t.test(x = x, alternative = "two.sided", conf.level =   0.95) %>%
  tidy() %>%
  select(estimate, p.value)
} 
```

The following code is a simulation of when mu = 0, 5000 datasets are generated by the model, and the estimate and p-value are obtained from a one-sample t-test.

```{r}
mu_0_simulation = rerun(5000, simulation_function(mu = 0)) %>%
bind_rows()

mu_0_simulation
```

The following code is a simulation for when mu is equal to 0 through 6, 5000 datasets are generated for each mu, and the estimate and p-value are obtained from a one-sample t-test.

```{r, message = FALSE, warning = FALSE}
mu_sim = tibble(mu = c(0,1,2,3,4,5,6)) %>%
  mutate(output = map(.x = mu, ~rerun(5000,
  simulation_function(mu = .x))),
  result = map(output, bind_rows)) %>%
  select(-output) %>%
  unnest()

mu_sim
```

## Plot 1

The following code is used to produce a plot that shows the proportion of times the null hypothesis was rejected and the true value of mu.  Based on the plot, one can observe that as the true mean increases, the power also increases.  Additionally, as the true mean increases, the effect size also increases.  Please note that the proportion of times the null hypothesis was rejected becomes relatively stable at around 1 for a true mean of 4, 5, and 6.

```{r}
null_reject_plot = 
  mu_sim %>%
  group_by(mu) %>%
  summarize(number = n(),
  p_value = sum(p.value < 0.05),
  proportion_null_reject = p_value/number) %>%
  ggplot(aes(x = mu, y = proportion_null_reject)) + 
  geom_point() +
  labs(
    x = "True Mean", 
    y = "Proportion of Times the Null Hypothesis Was Rejected",
    title = "Proportion of Times the Null Hypothesis Was Rejected Vs. True Mean"
  )

null_reject_plot
```

## Plot 2

```{r}
average_true_mean_plot = 
  mu_sim %>%
  group_by(mu) %>%
  summarize(estimate_average = mean(estimate)) %>%
  ggplot(aes(x = mu, y = estimate_average)) + 
  geom_point() +
  labs(
    x = "True Mean", 
    y = "Average Estimated Mean", 
    title = "Average Estimated Mean Vs. True Mean For All Samples"
  )

average_true_mean_plot 
```

## Plot 3

The sample average of mu across tests for which the null is rejected is approximately equal to the true value of mu.  However, it is important to note that when the true mean is equal to 1, the average estimated mean is about 2.25.  It is also important to note that when the true mean is equal to 2, the average estimated mean is about 2.5.  All of the other average estimated means are relatively more equal to the corresponding true mean, such as 0, 3, 4, 5, and 6.

```{r}
average_null_reject_plot =
  mu_sim %>%
  filter(p.value < 0.05) %>%
  group_by(mu) %>%
  summarize(estimate_average = mean(estimate)) %>%
  ggplot(aes(x = mu, y = estimate_average)) + 
  geom_point() +
  labs(
    x = "True Mean", 
    y = "Average Estimated Mean",
    title = "Average Estimated Mean vs. True Mean For Rejected Null Hypothesis Samples"
  )
  
average_null_reject_plot
```








